TEMPERATURES AND METALLICITIES FOR 10,000 M DWARFS\\ IN THE \apogee\ SURVEY

### 2018-09-20 paper/draft.tex
add radius to table

\item \textbf{Training bound selection:} Because extrapolation with \thecannon\ is unreliable, we select only sources with labels inside the range of the training sample: for the reported temperatures and metallicities we impose $2850<T_{\rm eff}<4150$ and $-0.5<[Fe/H]<0.5$, and for reported spectral subtypes we impose $0<SPT<9$.
\end{enumerate}

@@

\begin{deluxetable*}{rcl}
\tablecaption{Test results table header description.}
\tablehead{Column & Unit & Description}
\startdata
{\tt APOGEE$\_$ID} 	& 	& \apogee\ \zmass\ designation \\
{\tt BP$\_$MAG }		& mag	& \gaia\ $BP$ band photometry	\\
{\tt BP$\_$RP} 		& mag	& \gaia\ $BP-RP$ color	\\
{\tt CHI$\_$MANN} 	& 	& $\chi^2$ fit of Mann-trained \cannon\ model	\\
{\tt CHI$\_$WEST} 	& 	& $\chi^2$ fit of West-trained \cannon\ model	\\
{\tt DEC} 			& deg	& \apogee\ declination angle	\\
{\tt DIST} 			& pc	& Distance (1/$\varpi$)	\\
{\tt FE$\_$H }		& dex	& Mann-trained \cannon\ [Fe/H]	\\
{\tt GAIA$\_$ID} 		&	& \gaia\ identification number \\
{\tt G$\_$ABS} 		& mag	& \gaia\ $G$ band absolute magnitude	\\
{\tt G$\_$MAG} 		& mag	& \gaia\ $G$ band photometry	\\
{\tt H} 				& mag	& \apogee\ $H$ band photometry	\\
{\tt H$\_$ERR} 		& mag	& \apogee\ $H$ band photometry uncertainty	\\
{\tt J} 				& mag	& \apogee\ $J$ band photometry	\\
{\tt J$\_$ERR} 		& mag	& \apogee\ $J$ band photometry uncertainty	\\
{\tt K} 				& mag	& \apogee\ $K$ band photometry	\\
{\tt K$\_$ERR} 		& mag	& \apogee\ $K$ band photometry uncertainty	\\
{\tt PLX} 			& mas	& \gaia\ parallax	\\
{\tt PLX$\_$ERR} 		& mas	& \gaia\ parallax uncertainty	\\
{\tt PMDEC} 			& mas yr$^{-1}$	& \gaia\ declination proper motion	\\
{\tt PMDEC$\_$ERR} 	& mas yr$^{-1}$	& \gaia\ declination proper motion uncertainty	\\
{\tt PMRA} 			& mas yr$^{-1}$	& \gaia\ radial ascension proper motion	\\
{\tt PMRA$\_$ERR} 	& mas yr$^{-1}$	& \gaia\ radial ascension proper motion uncertainty	\\
{\tt RA} 				& deg	& \apogee\ radial ascension angle	\\
{\tt RP$\_$MAG} 		& mag	& \gaia\ $RP$ band photometry	\\
{\tt RV$\_$APOGEE} 	& km s$^{-1}$	& \apogee\ radial velocity	\\
{\tt RV$\_$APOGEE$\_$ERR} 	& km s$^{-1}$	& \apogee\ radial velocity uncertainty	\\
{\tt RV$\_$GAIA} 				& km s$^{-1}$	& \gaia\ radial velocity	\\
{\tt RV$\_$GAIA$\_$ERR}		& km s$^{-1}$	& \gaia\ radial velocity uncertainty	\\
{\tt SPT} 				& 	& West-trained \cannon\ spectral subtype ($M0-M9$)	\\
{\tt TEFF} 				& K	& Mann-trained \cannon\ effective temperature	\\
{\tt Vx} 				& km s$^{-1}$	& Cartesian $x$ velocity in Galactocentric coordnates	\\
{\tt Vy} 				& km s$^{-1}$	& Cartesian $y$ velocity in Galactocentric coordnates	\\
{\tt Vz} 				& km s$^{-1}$	& Cartesian $z$ velocity in Galactocentric coordnates	\\
{\tt X} 				& pc	& Cartesian $x$ position in Galactocentric coordnates	\\
{\tt Y} 				& pc	& Cartesian $y$ position in Galactocentric coordnates	\\
{\tt Z} 				& pc	& Cartesian $z$ position in Galactocentric coordnates	
\enddata
\end{deluxetable*}

>>>>

\item \textbf{Training bound selection:} Because extrapolation with \thecannon\ is unreliable, we select only sources with labels inside the range of the training sample: for the reported temperatures and metallicities we impose $2850<T_{\rm eff}<4150$ and $-0.5<$[Fe/H]$<0.5$, and for reported spectral subtypes we impose $0<SPT<9$.
\end{enumerate}

@@

\begin{deluxetable*}{rcl}
\tablecaption{Test results table header description.}
\tablehead{Column & Unit & Description}
\startdata
{\tt APOGEE$\_$ID} 	& 	& \apogee\ \zmass\ designation \\
{\tt BP$\_$MAG }		& mag	& \gaia\ $BP$ band photometry	\\
{\tt BP$\_$RP} 		& mag	& \gaia\ $BP-RP$ color	\\
{\tt CHI$\_$MANN} 	& 	& $\chi^2$ fit of Mann-trained \cannon\ model	\\
{\tt CHI$\_$WEST} 	& 	& $\chi^2$ fit of West-trained \cannon\ model	\\
{\tt DEC} 			& deg	& \apogee\ declination angle	\\
{\tt DIST} 			& pc	& Distance (1/$\varpi$)	\\
{\tt FE$\_$H }		& dex	& Mann-trained \cannon\ [Fe/H]	\\
{\tt GAIA$\_$ID} 		&	& \gaia\ identification number \\
{\tt G$\_$ABS} 		& mag	& \gaia\ $G$ band absolute magnitude	\\
{\tt G$\_$MAG} 		& mag	& \gaia\ $G$ band photometry	\\
{\tt H} 				& mag	& \apogee\ $H$ band photometry	\\
{\tt H$\_$ERR} 		& mag	& \apogee\ $H$ band photometry uncertainty	\\
{\tt J} 				& mag	& \apogee\ $J$ band photometry	\\
{\tt J$\_$ERR} 		& mag	& \apogee\ $J$ band photometry uncertainty	\\
{\tt K} 				& mag	& \apogee\ $K$ band photometry	\\
{\tt K$\_$ERR} 		& mag	& \apogee\ $K$ band photometry uncertainty	\\
{\tt PLX} 			& mas	& \gaia\ parallax	\\
{\tt PLX$\_$ERR} 		& mas	& \gaia\ parallax uncertainty	\\
{\tt PMDEC} 			& mas yr$^{-1}$	& \gaia\ declination proper motion	\\
{\tt PMDEC$\_$ERR} 	& mas yr$^{-1}$	& \gaia\ declination proper motion uncertainty	\\
{\tt PMRA} 			& mas yr$^{-1}$	& \gaia\ radial ascension proper motion	\\
{\tt PMRA$\_$ERR} 	& mas yr$^{-1}$	& \gaia\ radial ascension proper motion uncertainty	\\
{\tt RA} 				& deg	& \apogee\ radial ascension angle	\\
{\tt RADIUS} 			& R$_\odot$	& Radius determined by \citealt{Mann:2015} relation	\\
{\tt RP$\_$MAG} 		& mag	& \gaia\ $RP$ band photometry	\\
{\tt RV$\_$APOGEE} 	& km s$^{-1}$	& \apogee\ radial velocity	\\
{\tt RV$\_$APOGEE$\_$ERR} 	& km s$^{-1}$	& \apogee\ radial velocity uncertainty	\\
{\tt RV$\_$GAIA} 				& km s$^{-1}$	& \gaia\ radial velocity	\\
{\tt RV$\_$GAIA$\_$ERR}		& km s$^{-1}$	& \gaia\ radial velocity uncertainty	\\
{\tt SPT} 				& 	& West-trained \cannon\ spectral subtype (M0$-$M9)	\\
{\tt TEFF} 				& K	& Mann-trained \cannon\ effective temperature	\\
{\tt Vx} 				& km s$^{-1}$	& Cartesian $x$ velocity in Galactocentric coordnates	\\
{\tt Vy} 				& km s$^{-1}$	& Cartesian $y$ velocity in Galactocentric coordnates	\\
{\tt Vz} 				& km s$^{-1}$	& Cartesian $z$ velocity in Galactocentric coordnates	\\
{\tt X} 				& pc	& Cartesian $x$ position in Galactocentric coordnates	\\
{\tt Y} 				& pc	& Cartesian $y$ position in Galactocentric coordnates	\\
{\tt Z} 				& pc	& Cartesian $z$ position in Galactocentric coordnates	
\enddata
\end{deluxetable*}
